---
title: "General Linear Models for Detailed First Intervention"
output: rmarkdown::github_document
---

This file considers the actual number of blocks, instead of just the is_singleton indicator, in the first phase 3 intervention.

## Imports and helper function
```{r message=FALSE, warning=FALSE}
library(data.table)
library(magrittr)

getMetrics <- function (glmSumm) {
  metrics <- summary(glmSumm)$coefficients %>% as.data.table(keep.rownames = TRUE)
  metrics[, (2:ncol(metrics)) := lapply(.SD, function(x) round(x, 4)), .SDcols=2:ncol(metrics)]
  metrics
}

quizDT <- fread(file="../ignore/output/quiz_design_matrix.csv")
fquizDT <- fread(file="../ignore/output/f_quiz_design_matrix.csv")
taskDT <- fread(file = '../ignore/output/task_design_matrix.csv')
ftaskDT <- fread(file = '../ignore/output/f_task_design_matrix.csv')
```

## Predict First Intervention from Length and Functional Form
```{r}
mCombo <- glm(first_num_blocks ~ startswith_d * has_phase_2,
             data = taskDT,
             family = gaussian()
)

print.data.frame(getMetrics(mCombo))
```
```{r}
mCombo$df.residual
```

```{r}
fmCombo <- glm(first_num_blocks ~ startswith_d * has_phase_2,
             data = ftaskDT,
             family = gaussian()
)

print.data.frame(getMetrics(fmCombo))
```
```{r}
fmCombo$df.residual
```

## Predict Performance from First Intervention
```{r}
# join quiz and tasks
joinedDT <- taskDT[quizDT, on="session_id", nomatch=0]
fjoinedDT <- ftaskDT[fquizDT, on="session_id", nomatch=0]
```

### Blicket classification accuracy:
```{r}
mComboBlicket <- glm(accuracy ~ first_num_blocks*is_d3,
             data = joinedDT,
             family = binomial(link = "logit"),
             weights = rep(9, nrow(joinedDT))  # 9 block classifications
)

print.data.frame(getMetrics(mComboBlicket))
```

### **Filtered** blicket classification accuracy:
```{r}
fmComboBlicket <- glm(accuracy ~ first_num_blocks*is_d3,
             data = fjoinedDT,
             family = binomial(link = "logit"),
             weights = rep(9, nrow(fjoinedDT))  # 9 block classifications
)

print.data.frame(getMetrics(fmComboBlicket))
```

### Activation Prediction Accuracy
```{r}
mComboPred <- glm(total_points ~ first_num_blocks*is_d3,
             data = joinedDT,
             family = binomial(link = "logit"),
             weights = rep(7, nrow(joinedDT))  # 7 prediction questions
)

print.data.frame(getMetrics(mComboPred))
```

### **Filtered** Activation Prediction Accuracy
```{r}
fmComboPred <- glm(total_points ~ first_num_blocks*is_d3,
             data = fjoinedDT,
             family = binomial(link = "logit"),
             weights = rep(7, nrow(fjoinedDT))  # 7 prediction questions
)

print.data.frame(getMetrics(fmComboPred))
```